Hypertension and microbiome

### 2019-10-18 articletwo.Rmd
Diagnostic plot

```{r lacto deseq}
#dds.data.salt <- phyloseq_to_deseq2(pseq.genus.salt, ~ BL_AGE + SEX + NA.)
dds.data.salt <- phyloseq_to_deseq2(pseq.genus.salt, deseq.formula("NA.", var.CL))

dds.salt <- DESeq(dds.data.salt, test="Wald", fitType="parametric")

dset.genus.salt %>% pull(NA.) %>% mean

results(dds.salt, name = "NA.") %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    filter(Feature %in% "g_Lactobacillus") %>%
    kable
```

>>>>

```{r lacto deseq}
dds.data.salt <- phyloseq_to_deseq2(pseq.genus.salt, deseq.formula("NA.", var.CL))
dds.salt <- DESeq(dds.data.salt, test="Wald", fitType="parametric") 
```

```{r lacto deseq results}
dds.salt %>%
    results(., name = "NA.") %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    filter(Feature %in% "g_Lactobacillus") %>%
    kable
```

```{r lacto deseq diagnostic}
png("cache/salt-ma.png", width = 1200, height = 800, pointsize = 20)
par(mfrow=c(1,2))
plotMA(dds.salt)
plotDispEsts(dds.salt)
dev.off()
```

<img src = "cache/salt-ma.png" />
